%
% File eacl2017.tex
%
%% Based on the style files for ACL-2016
%% Based on the style files for ACL-2015, with some improvements
%%  taken from the NAACL-2016 style
%% Based on the style files for ACL-2014, which were, in turn,
%% Based on the style files for ACL-2013, which were, in turn,
%% Based on the style files for ACL-2012, which were, in turn,
%% based on the style files for ACL-2011, which were, in turn, 
%% based on the style files for ACL-2010, which were, in turn, 
%% based on the style files for ACL-IJCNLP-2009, which were, in turn,
%% based on the style files for EACL-2009 and IJCNLP-2008...

%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt,a4paper]{article}
\usepackage{acl2017}
\usepackage{times}
\usepackage{multirow}
\usepackage{url}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{color}
\usepackage{booktabs}

\aclfinalcopy % Uncomment this line for the final submission
%\def\eaclpaperid{***} %  Enter the acl Paper ID here

%\setlength\titlebox{5cm}
% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

\newcommand\BibTeX{B{\sc ib}\TeX}

\title{Vietnamese Text Classification System \\ in underthesea v1.1.7}

\author{
Vu Anh\\
underthesea\\
Hanoi, Vietnam\\
anhv.ict91@gmail.com
}
\date{}

\begin{document}
\maketitle
\begin{abstract}
In this report, we describe our classification system for Vietnamese, which is integrated in underthesea version 1.1.7

\end{abstract}

\section{Introduction}

Text classification is an important task in Natural Language Processing with many applications, such as web search, information retrieval, ranking and document classification.

In recent years, natural language processing and text classification have had a lot of works with encouraging results of research comminity in side and outsite Vietnam. The relevant works outside Vietnam have been published a lot.

\section{System Description}

We takes some experiments in Naive Bayes, SVM ~\cite{Suykens1999}, fasttext models ~\cite{DBLP:journals/corr/JoulinGBM16}.

\subsection{SVM}

SVM algorithm works by creating support vectors that separating two classes in n-dimensional space, where each dimension is represented by a feature. The separation is done by finding the largest separation margin between  the features from the two classes and a vector.

\subsection{FastText}

FastText maps each vocabulary to a real-valued  vector, with unknown words having a special vocabulary ID. A document can be represented as the average of all these vectors. Then FastText will train a maximum entropy multi-class classifier  on the vectors and the output labels.

\section{Evaluation}

\subsection{Data sets}

\noindent \textbf{TC201805}: This dataset contains 5000 items in 15 categories

\noindent \textbf{VNTC}: A Vietnamese corpus based on the four largest
circulation Vietnamese online newspapers: VnExpress, TuoiTre Online, Thanh Nien Online, Nguoi Lao Dong Online. The collected texts are automatically preprocessed (removing the HTML tags, spelling normalization) by Teleport software and various heuristics. There followed a stage of manual correction by linguists (five master students in Linguistics of University of Social Sciences, VNU-HCM city, Vietnam) who reviewed and adjusted the documents which are
classified to the wrong topics. Final relatively large and sufficient corpus includes about 100,000 documents.

\subsection{Evaluation Measures}

\subsection{Results}


\section{Conclusions}

To be updated

\bibliography{technique_report}
\bibliographystyle{acl_natbib}

\end{document}
